---
title: "COVID-19 Data Analysis"
author: "ILORI TOLULOPE VICTOR"
date: "`r Sys.Date()`"
output: html_document
---

## Introduction

This report presents a basic analysis of COVID-19 data in Nigeria using information from *Our World in Data*. I explore trends in confirmed cases and deaths to understand the progression of the pandemic in the country.
## Loading the Data

```{r load-packages, message=FALSE}
library(tidyverse)
library(janitor)
```

```{r load-data}
covid_data <- read_csv("C:/Users/drtol/Downloads/owid-covid-data.csv")
covid_data <- clean_names(covid_data)

glimpse(covid_data)
summary(covid_data)
```
## Filtering Nigeria's Data

```{r filter-nigeria}
nigeria_data <- covid_data %>%
  filter(location == "Nigeria")
```

## Daily New COVID-19 Cases

```{r plot-new-cases}
ggplot(nigeria_data, aes(x = date, y = new_cases)) +
  geom_line(color = "blue") +
  labs(title = "Daily New COVID-19 Cases in Nigeria",
       x = "Date", y = "New Cases")
```
## Total COVID-19 Deaths Over Time

```{r plot-total-deaths}
ggplot(nigeria_data, aes(x = date, y = total_deaths)) +
  geom_line(color = "red") +
  labs(title = "Total COVID-19 Deaths in Nigeria Over Time",
       x = "Date", y = "Total Deaths")
```

## Day With Highest New Deaths

```{r max-new-deaths}
nigeria_data %>%
  filter(new_deaths == max(new_deaths, na.rm = TRUE)) %>%
  select(date, new_deaths)
```

## Conclusion

In this project, I:

- Imported and cleaned the COVID-19 dataset  
- Filtered for Nigeria  
- Plotted new daily cases and total deaths over time  
- Identified the day with the highest number of new deaths



